---
title: "W_UP_01"
author: "Galilea Hernandez"
date: "fall 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

From observations the skill players seemed to perform more push ups than the line players

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
From observing the table, the line players had an average of push ups performed of 17. While the skill players had an average of 50.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```
Based on the inferential data, the hypothesis is "if skill players performed more push ups than line players, skill players position gave them an advantage over line players positions." The given hypothesis indicates that the difference in average between line players and skill players wasn't 0, while it wasn't zero there is a clear difference not only with the time in which the skill and line players did their push ups but also the amount. The position of the players creates a vast gap in push ups performed. the mean line in each group had a 95% difference which was incredibly high.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The data presented supports that the position difference of line vs skill players greatly affects the performance of push ups recorded from both the line and skill players. We saw that the Skill players had performed 33 more push ups in 18 minutes over the line players which had an average of 17 in 6 minutes. the relationship between the two can be asserted to the time in which the push ups were performed and the position of these players.